---
title: "Crypto_Lab"
author: "Dan Yang"
date: "5/21/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in library & dataset
```{r}
library(tidyr)
library(lubridate)
library(dplyr)
library(ggplot2)


setwd(getwd())
print(getwd())

#coins <- read.csv("data/coins.csv")
#coin_prices <- read.csv("data/crypto_rates.csv")

#synthesized version
coins <- read.csv("data_synthesized/coins.csv")
BTC_coin_prices_df <- read.csv("data_synthesized/BTC_coin_prices.csv")
BTC_coin_prices_df$dates <- ymd(BTC_coin_prices_df$dates)
DASH_coin_prices_df <- read.csv("data_synthesized/DASH_coin_prices.csv")
DASH_coin_prices_df$dates <- ymd(DASH_coin_prices_df$dates)
DOGE_coin_prices_df <- read.csv("data_synthesized/DOGE_coin_prices.csv")
DOGE_coin_prices_df$dates <- ymd(DOGE_coin_prices_df$dates)
ETH_coin_prices_df <- read.csv("data_synthesized/ETH_coin_prices.csv")
ETH_coin_prices_df$dates <- ymd(ETH_coin_prices_df$dates)
LTC_coin_prices_df <- read.csv("data_synthesized/LTC_coin_prices.csv")
LTC_coin_prices_df$dates <- ymd(LTC_coin_prices_df$dates)
XMR_coin_prices_df <- read.csv("data_synthesized/XMR_coin_prices.csv")
XMR_coin_prices_df$dates <- ymd(XMR_coin_prices_df$dates)


gpus <- read.csv("data_synthesized/gpus.csv")
gpu_prices <- read.csv("data_synthesized/gpu_rates.csv")
```

Build dataframes of historical prices of mineable coins from the dataset.
(For synthesizing, no need)
```{r}
coin_code2id <- t(filter(coins, Is_Mineable == 1)["Id"])
names(coin_code2id) <- as.character(t(filter(coins, Is_Mineable == 1)["Code"]))

#Coin Time-Price Data
build_coin_df <- function(cid) {
  data <- data.frame(
    dates=ymd(unlist(filter(coin_prices, CodeId == cid)["TimeId"])),
    coin_prices=unlist(filter(coin_prices, CodeId == cid)["Close"])
    )
  return(data)
}

for (code in names(coin_code2id)){
  dat <- build_coin_df(coin_code2id[code])
  assign(paste(code, "coin_prices", sep="_"), dat)
  write.csv(dat, paste("data_synthesized", paste(code, "coin_prices.csv", sep="_"), sep="/"))
}

#make gpu_prices smaller file for class
#aa <- unique(gpus$Id)
#class(aa)
#bb<- gpu_prices[gpu_prices$ProdId %in% aa, ]
#write.csv(bb, "gpu_prices_2.csv")

```

#Q1
Choose a model of GeForce Titan X GPUs  as your dependent variable and use historical price of btc as your independent variable and make a lm model.
```{r}
#helper func to get historical prices
gpu_hprice <- function(id) {
  hprices <- subset(gpu_prices, ProdId == id, 
                    select=c(TimeId, Price_USD)
                    )
  hprices$TimeId <- ymd(hprices$TimeId) #to "Date" class
  hprices <- rename(hprices, 
                    dates = TimeId,
                    gpu_prices = Price_USD
  )
  return(hprices)
}

titanx <- gpu_hprice(1975)

#merge gpuprice & btc price by date...results in many less data points
c <- merge(titanx, BTC_coin_prices_df, by="dates")

c <- merge(BTC_coin_prices_df, titanx, by="dates")

#plot price of titanx and btc over their time period
ggplot(c, aes(x=dates)) + 
  geom_line(aes(y=gpu_prices), color='red') + 
  geom_line(aes(y=coin_prices), color='blue') + 
  labs(x="Time", y="Price ($")

#build model
titanx_on_btc <- lm(gpu_prices ~ coin_prices, data=c)
summary(titanx_on_btc)

#plot trained model vs original
ggplot(data=c, aes(x = coin_prices, y = gpu_prices)) +
  labs(y = "GPU Price ($)",
       x = "Price of 1 BTC ($)") +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

#Report how many datapoints your model is based on, and what time period is the fit based on.
#Report your intuitions about this model.

#Residual Plot against predictors
ggplot(titanx_on_btc, aes(x=.fitted, y=.resid)) + 
  geom_point() + labs(x="Fitted", y="Residuals")
```

#Q2
Using 980Ti with id=1937, do a similar model as above but with all mineable coins as independent variables
```{r}
evga980ti <- gpu_hprice(1975)

bigdf <-  merge(titanx, BTC_coin_prices_df, by="dates")
bigdf <- merge(bigdf, DASH_coin_prices_df, by="dates", suffixes = c("_btc", "_dash"))
bigdf <- merge(bigdf, ETH_coin_prices_df, by="dates")
bigdf <- merge(bigdf, LTC_coin_prices_df, by="dates", suffixes = c("_eth", "_ltc"))
bigdf <- merge(bigdf, XMR_coin_prices_df, by="dates")
bigdf <- merge(bigdf, DOGE_coin_prices_df, by="dates", suffixes = c("_xmr", "_doge"))

#better but idk how to name them properly
#bigdf <- Reduce(function(...) merge(..., by="dates"), 
#                list(titanx, BTC_coin_prices_df, DASH_coin_prices_df,
#                     ETH_coin_prices_df, LTC_coin_prices_df,
#                     XMR_coin_prices_df, DOGE_coin_prices_df))

#Plot all prices over time
ggplot(bigdf, aes(x=dates)) + 
  geom_line(aes(y=coin_prices_btc, color='BTC')) + 
  geom_line(aes(y=coin_prices_dash, color='DASH')) + 
  geom_line(aes(y=coin_prices_eth, color='ETH')) + 
  geom_line(aes(y=coin_prices_ltc, color='LTC')) + 
  geom_line(aes(y=coin_prices_xmr, color='XMR')) + 
  geom_line(aes(y=coin_prices_doge, color='DOGE')) + 
  geom_line(aes(y=gpu_prices, color='GTX980Ti')) + 
  labs(x="Time", y="log(Price) ($)") + 
  scale_y_log10() 


evga980ti_on_allmine <- lm(gpu_prices ~ . - dates, data=bigdf)
summary(evga980ti_on_allmine)

GGally::ggpairs(bigdf, columns=2:8)

#Residual Plot against predictors
ggplot(evga980ti_on_allmine, aes(x=.fitted, y=.resid)) + 
  geom_point() + labs(x="Fitted", y="Residuals")
```

#Q3
```{r}
                                            # y0 depends on y0-1, for num lags, need y0-num past data points
btc_15_16 <- subset(BTC_coin_prices_df, dates >= "2014-12-27" & dates <= "2015-12-31") #enough for 5 lags,
for (i in 1:5) {
  btc_15_16 <- cbind(btc_15_16, lag(btc_15_16["coin_prices"], i))
  #name accordingly
  names(btc_15_16)[ncol(btc_15_16)] <- paste0("lag_", i)
}

#fit with yt = b0 + b1*yt-1 ... for 5 lags
ar5_15_16 <- lm(coin_prices ~ lag_1+lag_2+lag_3+lag_4+lag_5, data=btc_15_16)
summary(ar5_15_16)

#use fit to predict values in 16-17
btc_16_17 <- subset(BTC_coin_prices_df, dates >= "2015-12-27" & dates <= "2016-12-31") #enough for 5 lags
for (i in 1:5) {
  btc_16_17 <- cbind(btc_16_17, lag(btc_16_17["coin_prices"], i))
  #name accordingly
  names(btc_16_17)[ncol(btc_16_17)] <- paste0("lag_", i)
}
# predict prices for 2016-01-01 to 2016-12-31. Note 2016 is a leap year (366 days)
N <- nrow(btc_16_17)
pred_16_17_w_15_16 <- predict.lm(ar5_15_16, btc_16_17[6:N,])

#plot predicted, true, and past year's values over time
df_16_17_w_15_16 <- data.frame(time=btc_16_17[6:N, "dates"],
                               predicted=pred_16_17_w_15_16,
                               true=btc_16_17[6:N, "coin_prices"]
                               )
                               #true_prev=ulnum[2:366])

ggplot(df_16_17_w_15_16, aes(x=time)) +
  geom_line(aes(y=predicted), color='red') + #predictions
  geom_line(aes(y=true), color='blue')  #true of 16-17



```


#Q4
```{r}
btc_14_16 <- subset(BTC_coin_prices_df, dates >= "2013-12-02" & dates <= "2015-12-31") #enough for 30 lags,
for (i in 1:30) {
  btc_14_16 <- cbind(btc_14_16, lag(btc_14_16["coin_prices"], i))
  #name accordingly
  names(btc_14_16)[ncol(btc_14_16)] <- paste0("lag_", i)
}
N <- nrow(btc_14_16)

ar30_14_16 <- lm(coin_prices ~ . - dates, data=btc_14_16)
summary(ar30_14_16)

#use fit to predict values in 16-18
btc_16_18 <- subset(BTC_coin_prices_df, dates >= "2015-12-02" & dates <= "2017-12-31") #enough for 30 lags
for (i in 1:30) {
  btc_16_18 <- cbind(btc_16_18, lag(btc_16_18["coin_prices"], i))
  #name accordingly
  names(btc_16_18)[ncol(btc_16_18)] <- paste0("lag_", i)
}
# predict prices for 2016-01-01 to 2017-12-31. Note start at 31 because first 30 are lag info for y0 for y0 @ 2016-01-01
N <- nrow(btc_16_18)
pred_16_18_w_15_16 <- predict.lm(ar30_14_16, btc_16_18[31:N,])

#plot predicted, true, and past year's values over time
df_16_18_w_15_16 <- data.frame(time=btc_16_18[31:N, "dates"],
                               predicted=pred_16_18_w_15_16,
                               true=btc_16_18[31:N, "coin_prices"]
                               )
                               #true_prev=ulnum[2:366])

ggplot(df_16_18_w_15_16, aes(x=time)) +
  geom_line(aes(y=predicted), color='red') + #predictions
  geom_line(aes(y=true), color='blue')  #true of 16-17
```


Example of using differenced(lag()) data, no shift back because I don't know how. I saw a post on how to do it by progressively aggregating each term and stuff but I'm not entirely confident I understand it.
```{r}
btc_14_16 <- subset(BTC_coin_prices_df, dates >= "2013-12-02" & dates <= "2015-12-31") #enough for 30 lags,

#diffed daily
dif_btc_14_16 <- diff(as.numeric(unlist(btc_14_16["coin_prices"])), lag=1)
N <- length(dif_btc_14_16)
#lag1 <- lag(dif_btc_14_16, 1)
#lag2 <- lag(dif_btc_14_16, 2)
df_diff_lag <- data.frame(dates=btc_14_16[1:N, "dates"],
                          yt=dif_btc_14_16)

for (i in 1:30) {
  df_diff_lag <- cbind(df_diff_lag, lag(dif_btc_14_16, i))
  #name
  names(df_diff_lag)[ncol(df_diff_lag)] <- paste0("lag_", i)
}

#build model
lagged_ar30_14_16 <- lm(yt ~ . - dates, data=df_diff_lag)
summary(lagged_ar30_14_16)

#use model to predict
#dif predict data
dif_btc_16_18 <- diff(as.numeric(unlist(btc_16_18["coin_prices"])), lag=1)
N <- length(dif_btc_16_18)

df_diff_lag <- data.frame(dates=btc_16_18[1:N, "dates"],
                          yt=dif_btc_16_18)

for (i in 1:30) {
  df_diff_lag <- cbind(df_diff_lag, lag(dif_btc_16_18, i))
  #name
  names(df_diff_lag)[ncol(df_diff_lag)] <- paste0("lag_", i)
}

diflag_pred <- predict.lm(lagged_ar30_14_16, df_diff_lag)

#plot predicted, true, and past year's values over time
lol <- data.frame(time=df_diff_lag["dates"],
                               predicted=diflag_pred,
                               true=dif_btc_16_18
                               )
                               #true_prev=ulnum[2:366])

ggplot(lol, aes(x=dates)) +
  geom_line(aes(y=predicted), color='red') + #predictions
  geom_line(aes(y=true), color='blue')  #true of 16-17

# OK, so it works, but how do we transform it back? fuck getting too complicated
```



```{r}


```


